{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
added fullstop in footnote

The third rule introduces the dynamic creation of new threads. In this rule the function $fresh_{l}$
\footnote{It is assumed that $fresh_l \neq fresh_{l'} Leftrightarrow l \neq l'$}
takes a set of thread identifiers and returns a new thread identifier at level $l$ and $\lambda_{init} : \mathcal{P}
\rightarrow \text{LocState}$ produces an initial state with the program pointer at the given program point.
If the current instruction at program point $i$ is the \texttt{start} instruction, a new thread
identifier is picked w.r.t. the security level of $i$. The program counter of the current thread
is increased by one, to step to the next instruction. The resulting concurrent state includes the
updated state of the current thread and the initial state for the new thread. The global memory
is not modified and the history is extended with the current thread id and the security level of $i$.

>>>>

The third rule introduces the dynamic creation of new threads. In this rule the function $fresh_{l}$
\footnote{It is assumed that $fresh_l \neq fresh_{l'} Leftrightarrow l \neq l'$.}
takes a set of thread identifiers and returns a new thread identifier at level $l$ and $\lambda_{init} : \mathcal{P}
\rightarrow \text{LocState}$ produces an initial state with the program pointer at the given program point.
If the current instruction at program point $i$ is the \texttt{start} instruction, a new thread
identifier is picked w.r.t. the security level of $i$. The program counter of the current thread
is increased by one, to step to the next instruction. The resulting concurrent state includes the
updated state of the current thread and the initial state for the new thread. The global memory
is not modified and the history is extended with the current thread id and the security level of $i$.
